---
title: "HW5"
author: "Jinwoo Jeong"
date: '2022 4 7 '
output:
  pdf_document: default
  html_document: default
---

# Problem 1. 

LDA is used to minimized the mean and variance of each group for c0 c1 although logistic regression use maximum likelihood in beta0 beta1 

LDA/QDA is to separate group with overlapped part   

QDA perform better than LDA and logistic regression but need to evaluate on the larger model. 



# Problem 2. 

a)

$p(X) = \frac{0.37}{1+0.37} = 0.27$

27% of people will in fact default

b)


$\frac{0.16}{1-0.16} = 0.19$

19% is the odd that she will default


# Problem 3. 

```{r}
library(ISLR2)
library(corrplot)
data("Weekly")
```
a)
```{r}
summary(Weekly)
corrplot(cor(Weekly[,-9]), method="number")
```
There are significant linear relationship between Year and Volume. no other relationship showed up. 


b)


```{r}
Weekly.fit<-glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume , data = Weekly,family = binomial)
summary(Weekly.fit)
```

only lag 2 has the statistical significant at level of 0.05 rest of them fail to reject null hypothesis

c)

```{r}
logWeekly.prob= predict(Weekly.fit, type='response')
logWeekly.pred = ifelse(logWeekly.prob>0.5 ,  "Up", "Down")
table(logWeekly.pred, Weekly$Direction)
(54+557)/nrow(Weekly)
54/(54+430)
557/(48+557)

```
it shows that the model prediction of the weekly market trend 56.11% correctly. 
upward trends = 0.9206612
downward trends = 0.1115702

d)


```{r}
train = (Weekly$Year < 2009)
data0910 = Weekly[!train,]
Weekly.fit<-glm(Direction~Lag2, data=Weekly,family=binomial, subset=train)
logWeekly.prob= predict(Weekly.fit, data0910, type = "response")
logWeekly.pred = ifelse(logWeekly.prob>0.5 ,  "Up", "Down")
Direction.0910 = Weekly$Direction[!train]
table(logWeekly.pred, Direction.0910)
mean(logWeekly.pred == Direction.0910)
9/(34+9)
56/(56+5)
```
The model predict weekly trend with 62.5% correctly. Which is higher than previous model 
upward trends = 0.9180328
downward trends = 0.2093023

e)

```{r}
library(MASS)
lda.fit<-lda(Direction ~ Lag2, data = Weekly,family = binomial, subset = train)
Weeklylda.pred<-predict(lda.fit, data0910)
table(Weeklylda.pred$class, Direction.0910)
mean(Weeklylda.pred$class==Direction.0910)
9/(34+9)
56/(56+5)
```

performing LDA allows us to have similar results in part D.
upward trends = 0.9180328
downward trends = 0.2093023


f)

```{r}
qda.fit = qda(Direction ~ Lag2, data = Weekly, subset = train)
Weeklyqda.pred = predict(qda.fit, data0910)$class
table(Weeklyqda.pred, Direction.0910)
mean(Weeklyqda.pred==Direction.0910)
```

QDA predict model with 58.65% correctly it is lower than the LDA. it has only upward trends 
upward trends = 1


# Problem 4. 

```{r}
library(ISLR)
data("Auto")
summary(Auto)
```

a)
```{r}
mpg01 <- rep(0, length(Auto$mpg))
mpg01[Auto$mpg > median(Auto$mpg)] = 1
Auto = data.frame(Auto, mpg01)
```


b)
```{r}
corrplot(cor(Auto[,-9]), method="number")

```
For mpg01, mpg is positively correlated and cylinders, displacement, and weight are negatively correlated
horsepower(-) and origin(+) also has some correlation between mpg01


c)

```{r}
train = (Auto$year %% 2 == 0)
train.auto = Auto[train,]
test.auto = Auto[-train,]
```

d)

```{r}
autolda.fit <- lda(mpg01 ~ displacement + horsepower + weight + year + cylinders + origin, data = train.auto)
autolda.pred <- predict(autolda.fit, test.auto)
table(autolda.pred$class, test.auto$mpg01)
mean(autolda.pred$class != test.auto$mpg01)
```

The test error of the model is 8.44%


e)

```{r}
autoqda.fit <- qda(mpg01 ~ displacement + horsepower + weight + year + cylinders + origin, data = train.auto)
autoqda.pred <- predict(autoqda.fit, test.auto)
table(autoqda.pred$class, test.auto$mpg01)
mean(autoqda.pred$class != test.auto$mpg01)
```

The test error of the model is 9.97%


f)

```{r}
auto.fit<-glm(mpg01 ~ displacement + horsepower + weight + year + cylinders + origin, data=train.auto,family=binomial)
auto.probs = predict(auto.fit, test.auto, type = "response")
auto.pred = ifelse(auto.probs > 0.5, 1, 0)
table(auto.pred, test.auto$mpg01)
mean(auto.pred != test.auto$mpg01)
```

The test error of the model is 8.44%
